``TaylorScript'' is a \textbf{dynamic} and \textbf{procedural} programming langauge that draws inspiration from the well established langauges of Python, Java, and C. Our goal is to offer developers a coding experience that is not only accessible and user-friendly but also integrates the most valuable features from these renowned programming languages.

Designed to cater to a diverse audience, TaylorScript is a suitable for both seasoned developers and those new to the world of coding. Recognizing the challenges that newcomers often face, we have created an environment that eases the learning curve. For experienced developers, TaylorScript provides a powerful and efficient tool for a wide range of aplications.

The name TaylorScript is an homage to the global pop sensation, Taylor Swift. While not all members of our team may be Swifties, we collectively appreciate her significant contributions to the music industry. Taylor Swift's ability to tell compelling stories through her lyrics has inspired us to bring a touch of that artistic magic into the world of programming.

In tribute to Taylor Swift, we have integrated the titles of her albums and songs as keywords within TaylorScript. This unique approach adds a creative and personal dimension to the coding process, offering an enjoyable and inspiring medium for innovation. It's not just a programming language, it's a harmonious blend of art and technology, making "Taylor Script" a unique and engaging tool for developers who appreciate the connection between music and coding.
